Fusing Filters with Integer Linear Programming

### 2014-05-05 2014betterfusionforfilters/section/03-SizeInference.tex
Wibble

Although our constraint based formulation of size inference is reminiscent of type inference for HM(X)~\cite{odersky1999type}, there are important differences. Firstly, our type schemes include existential quantifiers, which represent the fact that the size of an arrays produced by filter operations are unknown in general. This is also the case for @generate@, where the result size is data dependent. HM(X) style type inferences makes use of an $\exists$ quantifier to bind local type variables in constraints, but they do not appear in type schemes. Secondly, our types are first order only, as program graphs cannot take other program graphs as arguments. Provided we generate the contraints in the correct form, solving them is straightforward.

>>>>

Although our constraint based formulation of size inference is reminiscent of type inference for HM(X)~\cite{odersky1999type}, there are important differences. Firstly, our type schemes include existential quantifiers, which represent the fact that the size of an arrays produced by filter operations are unknown in general. This is also the case for @generate@, where the result size is data dependent. HM(X) style type inferences uses the $\exists$ quantifier to bind local type variables in constraints, existential quantifiers do not appear in type schemes. Secondly, our types are first order only, as program graphs cannot take other program graphs as arguments. Provided we generate the constraints in the correct form, solving them is straightforward.
